Recruiting Chapter

### 2021-05-04 educ250c_presentation.Rmd
edit formatting of educ250c

---
title: "Recruiting Chapter"
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castaneda
date: 
urlcolor: blue
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true # toc_float option to float the table of contents to the left of the main document content. floating table of contents will always be visible even when the document is scrolled
      #collapsed: false # collapsed (defaults to TRUE) controls whether the TOC appears with only the top-level (e.g., H2) headers. If collapsed initially, the TOC is automatically expanded inline when necessary
      #smooth_scroll: true # smooth_scroll (defaults to TRUE) controls whether page scrolls are animated when TOC items are navigated to via mouse clicks
    number_sections: true
    fig_caption: true # ? this option doesn't seem to be working for figure inserted below outside of r code chunk    
    highlight: tango # Supported styles include "default", "tango", "pygments", "kate", "monochrome", "espresso", "zenburn", and "haddock" (specify null to prevent syntax    
    theme: default # theme specifies the Bootstrap theme to use for the page. Valid themes include default, cerulean, journal, flatly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti.
    df_print: tibble #options: default, tibble, paged
bibliography: ./other/burd_recruiting_chapter.bib
csl: ./other/apa.csl
---

@@

#pct_budget
#str(pct_budget)
#attributes(pct_budget)
kable(
  x = pct_budget, 
  col.names = c("Activity", "Private", "Public"),
  caption = "Percentage of budget allocated to marketing/recruiting activities by private non-profit 4yr and public 4yr institutions"
)
#  <div id="refs"></div>
```

@@

Number of events by type and in-state, out-of-state for public research universities institutions
```{r event-count-figure-pubu, echo = FALSE, out.width="125%"}
knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
```

@@

Number of events by type and in-state, out-of-state for private institutions
```{r event-count-figure-privu, echo = FALSE, out.width="125%"}
knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
```

@@

Actual versus proportional visits to out-of-state private high schools for public research universities
```{r, echo = FALSE, out.width="125%"}
knitr::include_graphics('assets/figures/figure_5.pdf')
```

@@

CRYSTAL - CAN YOU ADD FOLLOWING FIGURES CURRENTLY INCLUDED IN MANUSCRIPT.PDF

- FIG 7, CHARACTERISTICS OF PRIVATE HS VISITED BY PRIVATE INSTITUTIONS
- FIG 11, CHARACTERISTICS OF PRIVATE HS VISITED BY PUBLIC INSTITUTIONS

@@

CYSTAL - CAN YOU ADD FOLLOWING FIGURES CURRENTLY INCLUDED IN MANUSCRIPT.PDF

- FIG 10, 1-mode network for public institutions, colored by cluster
- FIG 12, 1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster

>>>>

---
title: "Recruiting Chapter"
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castaneda
date: 
urlcolor: blue
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 2
    toc_float: true # toc_float option to float the table of contents to the left of the main document content. floating table of contents will always be visible even when the document is scrolled
      #collapsed: false # collapsed (defaults to TRUE) controls whether the TOC appears with only the top-level (e.g., H2) headers. If collapsed initially, the TOC is automatically expanded inline when necessary
      #smooth_scroll: true # smooth_scroll (defaults to TRUE) controls whether page scrolls are animated when TOC items are navigated to via mouse clicks
    number_sections: true
    fig_caption: true # ? this option doesn't seem to be working for figure inserted below outside of r code chunk    
    highlight: tango # Supported styles include "default", "tango", "pygments", "kate", "monochrome", "espresso", "zenburn", and "haddock" (specify null to prevent syntax    
    theme: default # theme specifies the Bootstrap theme to use for the page. Valid themes include default, cerulean, journal, flatly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti.
    df_print: tibble #options: default, tibble, paged
bibliography: ./other/burd_recruiting_chapter.bib
csl: ./other/apa.csl
---

<style>
embed {
  width: 745px;
  height: 1000px;
}

#rq2-characteristics-of-visits-to-private-high-schools embed {
  width: 690px;
  height: 735px;
}

#rq3-overlapping-networks-of-visits-to-private-high-schools embed {
  width: 750px;
  height: 590px;
}

caption {
  color: black;
  font-weight: bold;
  white-space: pre !important;
} 
</style>

@@

#pct_budget
#str(pct_budget)
#attributes(pct_budget)
kable(
  x = pct_budget, 
  col.names = c("Activity", "Private", "Public"),
  caption = "Percentage of budget allocated to marketing/recruiting activities by private non-profit 4yr and public 4yr institutions"
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = F, position = "left")
#  <div id="refs"></div>
```

@@

**Number of events by type and in-state, out-of-state for public research universities institutions**

```{r event-count-figure-pubu, echo = FALSE}
knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
```

@@

**Number of events by type and in-state, out-of-state for private institutions**

```{r event-count-figure-privu, echo = FALSE}
knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
```

@@

**Actual versus proportional visits to out-of-state private high schools for public research universities**

```{r, echo = FALSE}
knitr::include_graphics('assets/figures/figure_5.pdf')
```

@@

**Characteristics of private HS visited by private institutions**

```{r ego-network-figure-privu, echo = FALSE}
knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
```

<br><br>

**Characteristics of private HS visited by public institutions**

```{r ego-network-figure-pubu, echo = FALSE}
knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
```

@@

**1-mode network for public institutions, colored by cluster**

```{r plot-1mode-pubu, echo = FALSE}
knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
```

<br><br>

**1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster**

```{r plot-1mode-all-pubu-outst, echo = FALSE}
knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
```
